Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-21 Report/review_comments.tex
changes with satya

>>>>

\subsection*{Reveiewer comments - \me{2}}

\cmnt The logic from (6) to (16) is not clear. The only difference is the two newly introduced NON-CONVEX constraints (16b) and (16c), while the objective function (16a) and the constraint (16d) is the same as (6). The equivalence between (6) and (16) is not straightforward and it is confusing why the reformulation in (16) is beneficial.

\cmnt The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex. Inspecting (19), its objective function is the same as in (6), and the non-convexity of (6) comes exactly from the objective function, so (19) is not a convex problem. The same flaw is repeated several times in the approximate problems proposed by the authors.

\cmnt The authors proposed to use block coordinate descent method to solve (16). But as the authors have already pointed out, to apply block coordinate descent method, the constraint sets for different variables should be disjoint (uncoupled), which is however not the case in (16), because receive and transmit precoders (i.e w and m) are coupled in the constraints. It is confusing on its own why the authors made a statement that contradicts the proposed methodology, and the convergence followed is in question.

\cmnt Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27]. In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.

\cmnt The authors also cited [28] to establish the convergence of SCA. But the techniques of [27] and [28] are different, and the convergence conditions are different too. It is not clear why the authors need two set of convergence conditions for a single problem, and the resulting convergence analysis itself is not solid enough.

\cmnt Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).

\cmnt The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13]. So the convergence analysis is not trustworthy.

\cmnt The length of the paper is too extensive. Some of the reformulations as mentioned in the previous comment can be skipped. Also, Section III.D. is not deeply explained and does not bring additional value to the paper. The implications of ordering the sub-channels for the iterative approach should be carefully studied and extensively explained in a different publication.

\cmnt Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).

\cmnt In Fig. 1 and Fig. 2, the labels for the system model do not fit with the written description. Additionally, the reference scheme Q-WSRM is not optimal, since it over allocates resources if there are few queued packets. Therefore, it is not interesting for comparison purposes.

\cmnt Assuming that Fig. 2 and Fig. 3 where obtained based on the same simulation setup, i.e. user queues, number of transmit and receive antennas and number of base stations, it is not clear why results in Fig. 3 are worse than Fig. 2 when comparing JSFRA. Even more, since the number of sub-channels is larger in Fig. 3, the result seems contradictory.

\subsection*{Reveiewer comments - \me{3}}

\cmnt This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods. This is an interesting and important topic.

\resp We thank the reviewer for reading the manuscript and providing valuable comments.

\cmnt 1. The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.

\resp Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression. It is necessary in case of the MSE formulation, where we have explicitly stated the optimization variable \me{t_k}. If the reviewer insist on replacing the rate expression using \me{t_k}, we can make those changes.

\cmnt 2. The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5). This is not obvious. An easy case to check this statement is that assuming the system has two BS and each BS serves one user. When \me{Q_1=0} and 2nd BS has sufficiently large power, (16b) and (16c) do not hold equality. Rigorous proof is needed if authors stick to this statement.

\resp We thank the reviewer for the insightful comment. We modified the statement such that it is an under estimator for the actual SINR expression and will be tight when the system is limited by the transmit power.

\cmnt 3. The solution in (21) is obtianed for MMSE, i.e. for 2-norm(q=2). If \me{q=1} or \me{q=\infty}, it is actually an equivalent linear programming problem. Details for this solution should be provided.

\resp We thank the reviewer for the critical comment. We have update the manuscript to include the information about the receiver with other q values. Please note that the receive beamformer doesn't depend on the q value explicitly. It depends inherently through the transmit precoders.

\cmnt 4. The convergence proof need to be rigorous. The inequality of (23a) is opposite to the reference [28]. Also the statement on uniqueness of the transmit and the receive beamformers are not correct. Although we can choose one antenna to be real value, this does not mean the problem has unique solution!

\cmnt 5. (25) is generally wrong. (25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion). This is clearly stated in the reference [5] and [6]. This can also be easily checked by comparing (25) and (2). Consequently the alternative formulation (26) based on this conclusion is questionable.

\resp We thank the reviewer for pointing out the information loss in the statement. We have provided more detail in the manuscript. The relation is valid if the receiver is based on the MMSE criterion. Note that, the receiver does not depend on the \me{q} value used in the objective. It depend only on the transmit precoders which in fact change based on the \me{q} value used in the objective function.

\cmnt 6. For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed. 1. The numbers of transmitted packets for users  \me{t_k}'s are optimization variables. So they should be explicitly stated in the problem formulation (6), (16), (20) and (26) to avoid confusing.

\subsection*{Reveiewer comments - \me{4}}

\cmnt First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method. "The SCA method" is often referred to, but never really defined or referenced. The three required conditions (as stated on p. 6, col. 1, rows 38-40) do not, as far as I can tell, appear in [27]. Indeed, [27] is concerned with optimization problems where the objective function is non-convex, but the constraint set is convex and separable over the blocks of variables. Perhaps you meant to cite [A], wherein non-convex constraints are handled in a similar way? Numerically, the algorithms do converge, and the argument put forward makes sense, but the treatment must be improved to be more rigorous.

\cmnt Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates. This is due to how the conditional Lyapunov drift is minimized. This approach completely removes the queue dynamics from the optimization problem, essentially leading to greedy one-shot optimization in 7
every time instant. The framework would be more interesting if some sort of optimization (or tracking) is performed over several time instants, rather than the one-shot approach that is currently used for the JSFRA algorithms. Possibly, some expectation over the queues would be optimized then. Even if no analytical treatment of the tracking over several time-steps is added, I would at least highly recommend adding some simulation results where the proposed one-shot algorithms are performed sequentially over several time instants.

\cmnt Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results. This reviewer recommends spending more space on the convergence, than on the description of the distributed techniques. Still, it would be nice with a direct description of what local CSI is required, and how it is acquired, to perform the local computations for the primal decomposition and ADMM methods. For the description of the signaling of the CSI in Sec. IV-B, are you envisioning a TDD system?

\cmnt Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier. This could easily be clarified.

\cmnt - p. 1, col. 1, row 42: "userss"

\resp Modified.

\cmnt - p. 1, col. 2, row 18: the precoders are used \_implicitly\_ as decision variables. This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.

\resp We thank the reviewer for the insightful comment on the proposed approach. We have modified the text accordingly.

\cmnt - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?

\resp We understand the reviewer's concern. We have provided the valid reference for the SCA scheme.

\cmnt - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead

\resp Changed.

\cmnt - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here

\resp We thank the reviewer for the concern on the grouped variable. We have modified the expressions accordingly.

\cmnt - p. 3, col. 2, row 26: Which general MIMO-OFDM problem are you talking about here, and what is combinatorial about it? Is it the problem of selecting users to be served on orthogonal subcarriers? There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.

\resp We thank the reviewer for the comment. We have removed the word "combinatorial" from the text.

\cmnt - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.

\resp It is restructured to include additional details.

\cmnt - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).

\resp Agreed.

\cmnt - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).

\cmnt - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.

\cmnt - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??

\resp We thank the reviewer for pointing out the mistake. We have modified accordingly to the comment.

\cmnt - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).

\cmnt - p. 6, col. 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs. However, does it affect the convergence of the algorithm?

\cmnt - p. 6, col. 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs. However, does it affect the convergence of the algorithm?

\resp We thank the reviewer for the comment.

\cmnt - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?

\cmnt - p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?

\resp We thank the reviewer for informing the important argument. The relaxed sub problem is strongly convex, due to the presence of norm function in the objective. Since the relaxation forced \me{q_{l,k,n} = 0}, the precoders are unique.

\cmnt - Table 1: "backpreassure"

\resp Changed in the revised manuscript

\cmnt - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.

\resp Changed in the revised manuscript

### 2015-01-21 Report/simulation_distributed.tex
changes with satya

The performances of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d} compares the performances of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.

>>>>

The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.

### 2015-01-21 Report/simulation_results.tex
changes with satya

We discuss the performance of the centralized algorithms in Section \ref{sec-3} for some system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively. 
\begin{table*}
	\centering
		\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpreassure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1} \vspace{-0.1in}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates}
	\label{fig-a} \vspace{-0.1in}
\end{figure*}

@@

For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component. Fig. \subref*{fig-1} shows the performances of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.

The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig. \ref{fig-a}. The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.

>>>>

We discuss the performance of the centralized algorithms in Section \ref{sec-3} for some system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively. 
\begin{table*}
	\centering
		\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1} \vspace{-0.1in}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates}
	\label{fig-a} \vspace{-0.1in}
\end{figure*}

@@

For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component. Fig. \subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.

The performance of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig. \ref{fig-a}. The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. All the algorithms are Pareto-optimal and provide different performance based on the weights used to find a point in the rate region.

### 2015-01-21 Report/sub_channel_wsrm.tex
changes with satya

The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation. In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size. In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation. The optimal approach is to decompose the problem over each sub-channel with a fixed transmit power constraint for each sub-channel. The power allocated for each sub-channel is controlled by a master problem based on different algorithms as discussed in \cite{palomar2006tutorial,boyd2011distributed}.

The proposed \acl{QM} \ac{SRA} formulation enables us to solve for the transmit precoders of all the users associated with the coordinating \ac{BS} in the set \me{\mathcal{B}} over each sub-channel independently by fixing the transmit power on each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}. In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization. The total number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}. However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem. 
%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
%\begin{algorithm}
% \SetAlgoLined
% \DontPrintSemicolon
% \BlankLine
% \SetKwInput{KwInit}{Initialize}
% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
% initialize \me{j = 0}\;
% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
% $j = j + 1$\;
% }
% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
% $i = i + 1$\;
% }
% }
% \caption{Algorithm of \acs{SRA} scheme}
% \label{algo-5}
%\end{algorithm}
%

>>>>

The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation. In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size. In order to mitigate this, we can adopt the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed} to distribute the precoder design across each sub-channels independently with some coupling parameters that are exchanged across the sub-channel wise subproblems.

As an alternative sub-optimal solution, we propose \acl{QM} \ac{SRA}, which aims at designing the precoders independently across each sub-channel in a sequential manner by taking the current backlogged packets into account. In this approach, the transmit power is fixed across each sub-channel \me{n} as \me{P_{\max,n}} at each \ac{BS}. The power split can either follow equal sharing or any predetermined pattern as in partial frequency reuse. For the fixed sub-channel power, the \ac{JSFRA} formulation presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} is performed over each sub-channel in a sequential manner. The coupling variable across the sub-channel is the total number of backlogged packets associated with each user. 
Let \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. Now, for the first sub-channel, \me{n=1}, the queues are given by \me{Q_{k,n=1} = Q_k}, which corresponds to the actual number of backlogged packets present in the current instant \me{i}. Using the updated number of queued packets, the \ac{JSFRA} algorithm is performed over the sub-channel \me{n=1} to obtain the rates associated with each user. Now, for \me{n=2}, the number of queued packets for each user is updated as \me{Q_{k,n=2} = Q_k - \sum_{l=0}^L t_{l,k,n=1}}. With this updated number of queued packets, the \ac{JSFRA} algorithm is performed for \me{n=1} sub-channel to obtain the optimal precoders. In general, the number of queued packets to be used for each user in a given sub-channel \me{n} is given by
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}.
\label{eqn-weight}
\end{equation}
In \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}. However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.

The proposed \ac{QM} \ac{SRA} scheme depend on the choice of the sub-channel selection, which is evident from the sequential approach used in the sub-optimal problem formulation. However, the proposed approach provides faster convergence in contrast to the \ac{JSFRA} formulation over all sub-channel mainly due to the reduction in the size of the sub-channel wise sub problem. The choice of the sub-channel selection is random and it is difficult to determine the order, since the optimization variables \me{\mvec{m}{l,k,n}} are vectors.
%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
%\begin{algorithm}
% \SetAlgoLined
% \DontPrintSemicolon
% \BlankLine
% \SetKwInput{KwInit}{Initialize}
% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
% initialize \me{j = 0}\;
% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
% $j = j + 1$\;
% }
% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
% $i = i + 1$\;
% }
% }
% \caption{Algorithm of \acs{SRA} scheme}
% \label{algo-5}
%\end{algorithm}
%
